\chapter{Conclusion and Future Recommendation}
\thispagestyle{empty}
Modern era mostly depends on Human-Computer Interaction (HCI). For a successful human-computer interaction, it is much needed for the computer to know the emotional state of the person with whom it is interacting from the person's facial expression. Facial Expression Recognition system plays a vital role in that task by identifying the emotion. In this chapter we conclude our work by mentioning the limitations and the scope for further improvements\par

\section{Conclusion}
In our work we tried to find the facial expression of a person from a given static image. The image was preprocessed and passed through the classifier to successfully understand the emotional state of that person. We implemented the classifier using two different methods and achieved a remarkable result on both of them. Our system can even identify the facial expression of bearded face images which will help in achieving a better communication among robots and peoples from all over the world.\par
Sometimes even for human it is very difficult to understand the expression from a given image. Since the emotion of a person is not always visible on their face, to exactly identify the emotion we need to know about the environment and the current situation of that the person. So, we can say that expression recognition may help in understanding the current state of a person more efficiently, but does not guaranteed that this is the exact emotion of that person. In near future the world will be more dependent on machine and a facial expression recognizer can help that machine to better understand humans and act accordingly.

\section{Future Recommendation}
Expression recognition from all face images is a challenging job. For recognizing the expression on bearded face, we didn't find any online dataset. So, we created our dataset for bearded face. But size of our collected bearded face dataset wasn't that large. There are some options where our FER system can be improved. Some future recommendations for our system are briefly described below:

\begin{itemize}
    \item Enrich the labeled dataset for bearded face image.
    \item Create a graphical user interface for identifying the expression on any image.
    \item Upgrade the system for identifying facial expression in real time.
    \item Add the information about the persons state and environment to better understand the persons emotion.
\end{itemize}

